---
title: "Beamer presentations"
author: "Austin Hart, Ph.D."
institute: "ahart@american.edu"
output:
  beamer_presentation:
    theme: "Malmoe"
    colortheme: "beaver"
fontsize: 11pt
classoption: "aspectratio=169"
---

```{r setup, include=FALSE}
## Libraries
  library(knitr)
  library(rmdformats)
  library(tidyverse)

## Global options
knitr::opts_chunk$set(
  echo = FALSE, 
  prompt = FALSE,
  tidy = FALSE, 
  comment = NA,
  message = FALSE, 
  warning = FALSE,
  fig.align = 'center'
)
```

# Welcome to beamer!

## Getting started

- Start a new RProject  
- Create a new R Markdown file:   

> New File -> RMarkdown -> Presentation -> PDF (Beamer)   

- Make your presentation   
- `Knit` to `.pdf` slides


## YAML options


Specify the `beamer_presentation` output, which knits to `.pdf`

Set your custom themes. See [classic theme options](https://hartwork.org/beamer-theme-matrix/).

```yaml
---
title: "Beamer presentations"
author: "Austin Hart, Ph.D."
institute: "ahart@american.edu"
output:
  beamer_presentation:
    theme: "Malmoe"
    colortheme: "beaver"
fontsize: 12pt
classoption: "aspectratio=169"
---
```

## Setup chunk

- Knitting initiates a new R environment. 
- Your `.Rmd` must be self-contained.
- Define the `knit` in a setup chunk. 
- Also the place to load packages, data, etc. 

## Example setup

```{r, eval = F, echo = T}
## Global options
  knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    fig.align = 'center' 
  )

## Packages
  library(tidyverse)
  library(knitr)

## Load data? Set themes?
```

## Defining new slides

- Initiate new slide with `##` Level 2 heading.  
- Use Level 1 (`#`) for BIG section slides

```{r, echo = T, eval = F}
## Title of slide 1
- Roadmap. 
- Materials.

## Slide 2
> Inspirational quote

## Slide 3  
### Subtitle
)
```

# Big section change

## No easy column splits

One downside is that columns splits are very tough.

A graph to ease the pain.

```{r, fig.dim=c(3,2)}
  mtcars |>
    ggplot(aes(x = mpg)) +
    geom_histogram(color = 'white', bins = 12) +
    theme_classic(base_size = 9) +
    scale_y_continuous(expand = expansion(mult = c(0,.01)))
```

## Basic reminders

### Level 3 header

If you want to write text, just write text.

- Itemized list  
  - Start with a `-` or `*` and type.  
  - Need two spaces or hard return between items.  
  
*Fancy italic* text.  
**Shouty bold** text.



